Notes on QM in generalized coordinates

### 2023-01-23 Notes/2023-QuantumGeneralizedCoordinates/QuantumGeneralizedCoordinates.tex
Adding ideas for cross check

TODO: Need a cross check with the transformation rule of momentum

>>>>

TODO: Need a cross check with the transformation rule of momentum. For example, show that the inner product in momentum basis is invariant:
\begin{equation}
	\begin{aligned}
		\int \phi^\dagger(p_j) \phi(p_j) dp^n &= \int \hat{\phi}^\dagger(\hat{p}_i) \phi(\hat{p}_i) d\hat{p}^n  \\
	\end{aligned}
\end{equation}
Another idea, show that applying the momentum operator in the new coordinates is equal to applying the the one in the old coordinates and then rescaling by the square root of the Jacobian.
